Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Minor tweak to wording

While data adopted for the given assessment are said to be accurate up to 15m from Mean Sea
Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for
this study. These are outlined further in the Discussion. Notably, the adopted depth
estimates were derived from bathymetries based on satellite imagery. Available data can be
limited in their alignment with the established GBRMPA reef outlines used to characterise
reef locations. Quality control flags were assigned to identify potential data limitations:
reefs with no overlapping bathymetry data, reefs with minimum depth values above sea level
(indicating potential data artifacts), and reefs where bathymetry pixels covered less than
5% of the reef polygon area. This removed 842 reefs, or 22%, from the initial set of 3806
reefs. Furthermore, reefs that are not associated with GBRMPA management areas [@GBRMPA2024]
or reefal bioregions [@GBRMPA2001] were also removed from the investigation. Bioregions
which contained fewer than three reefs were also excluded. As a result, 1377 reefs were
excluded (36%), leaving a total of 2429 remaining for the purpose of this investigation.

@@

![Median depth for reefs within each bioregion, separated into clusters assigned by
timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
are clusters with intermediate median area-relative cover between 2030 and 2040 within each
bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
width="14.82cm"}

>>>>

While data adopted for the given assessment are said to be accurate up to 15m from Mean Sea
Level [@GBRMPA2020], there are many sources of uncertainty in the depth estimates used for
this study. These are outlined further in the Discussion. Notably, the adopted depth
estimates were derived from bathymetries based on satellite imagery. Available data can be
limited in their alignment with the established GBRMPA reef outlines used to characterise
reef locations and their areal extent. Quality control flags were assigned to identify
potential data limitations: reefs with no overlapping bathymetry data, reefs with minimum
depth values above sea level (indicating potential data artifacts), and reefs where
bathymetry pixels covered less than 5% of the reef polygon area. This removed 842 reefs, or
22%, from the initial set of 3806 reefs. Furthermore, reefs that are not associated with
GBRMPA management areas [@GBRMPA2024] or reefal bioregions [@GBRMPA2001] were also removed
from the investigation. Bioregions which contained fewer than three reefs were also
excluded. As a result, 1377 reefs were excluded (36%), leaving a total of 2429 remaining for
the purpose of this investigation.

@@

![Median depth for reefs within each bioregion, separated into clusters assigned by
timeseries clustering. ‘Low’ clusters (green) are clusters with the lowest median
area-relative cover between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange)
are clusters with intermediate median area-relative cover between 2030 and 2040 within each
bioregion. ‘High’ clusters (blue) are clusters with the highest median area-relative cover
between 2030 and 2040 within each bioregion. Solid lines represent the median depth for each
cluster. Displays results for ACCESS-ESM1-5
GCM.](../outputs/ADRIA_results/HighResCoralStress/figs/ACCESS-ESM1-5/bioregion/depth_bioregion_violin.png){#fig-access-esm1-5-bioregion-depth
fig-align="center" width="14.82cm"}
